Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-16 ms.tex
clean-up

\subsection{CMB Removal}
The CMB is effectively imperceptible at 857 GHz, but can be noticed at a 
low level at 545 GHz, and is prominent at 217 GHz and 353 GHz relative 
to the diffuse Galactic emission we wish to characterize, especially at high
latitudes. To remove the CMB anisotropies, we have subtracted the SMICA model
from each of the relevant \PLANCK~maps \citep{smica}, after appropriate unit conversions.

@@

\subsection{Zero-Point}
Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components. At each frequency, there can
exist an overall, constant offset that must be subtracted to set the
zero level of Galactic dust. Additionally, faint residuals 
of the Solar dipole remain at low frequencies. At 353 GHz, 545 GHz, 857 GHz, 
we have adopted the zero-point offsets of \cite{planckdust} Table 1, which 
were derived by correlating \PLANCK~857 GHz versus HI at low column density, 
and then by correlating the other Planck channels against the corrected 857 
GHz map. We have not altered the \verb|i100| zero-point in any way. We have
also removed the Solar dipole residual according to \cite{planckdust}, 
by subtracting a dipole pattern oriented toward $(l, b) = ()$ and scaled
according to their Table 1.

>>>>

\subsection{CMB Removal}
The CMB is effectively imperceptible at 857 GHz, but can be noticed at a 
low level at 545 GHz, and is prominent at 217 GHz and 353 GHz relative 
to the diffuse Galactic emission we wish to characterize, especially at high
latitudes. To remove the CMB anisotropies, we have subtracted the SMICA model
from each of the relevant \PLANCK~maps \citep{smica}, after appropriate unit 
conversions. Removal of the residual Solar dipole at low frequencies is 
discussed in $\S$\ref{sec:zp}.

@@

\subsection{Zero-Point}
\label{sec:zp}
Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components on large angular scales. At each 
frequency, there can exist an overall, constant offset that must be subtracted 
to set the zero level of Galactic dust. Additionally, faint residuals of the 
Solar dipole remain at low frequencies. At 353 GHz, 545 GHz, 857 GHz, we have 
adopted the zero-point offsets of \cite{planckdust} Table 1, which were derived
 by correlating \PLANCK~857 GHz versus HI at low column density, and then by 
correlating the other Planck channels against the corrected 857 GHz map. We 
have not altered the \verb|i100| zero-point in any way. We have also removed 
the Solar dipole residual according to \cite{planckdust}, by subtracting a 
dipole pattern oriented toward $(l, b) = ()$ and scaled according to their 
Table 1.
